Arrows for Parallel Computations

### 2017-08-16 paper/content/benchmarks.tex
minor

%
\section{Performance results}
\label{sec:benchmarks}

\newcommand{\rmtest}{Rabin--Miller test\xspace}
\newcommand{\torustest}{Torus Matrix Multiplication test\xspace}
\newlength{\plotwidthSMP}
\setlength{\plotwidthSMP}{0.39\textwidth}
\newlength{\plotwidthDist}
\setlength{\plotwidthDist}{0.6\textwidth}

@@

\begin{figure}
%\centering
%\performanceSkelRMSM{11213}{64}\hfill%
{\speedupSkelRMSM{11213}{32}}\hfill%
{\speedupSkelRMSM{11213}{64}}
\caption{Relative speedup of \rmtest on a multicore machine. We used the same PArrows-based implementation with
  different backends on the same hardware. Measurements were performed on a single node of Glasgow
  grid; it has 16 real cores. Input was $2^{11213}-1$, we used 32 (left) or 64 (right)
  tasks. The
  closer to linear speedup the better.}
\label{fig:bench-rm-sm}
\end{figure}

@@

\newcommand{\speedupSudokuSM}[1]{
\speedupplot{Speedup of \rmtest ``#1''}{Eden CP, Multicore, Par Monad, Par Monad (vanilla)}{16}{4}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-eden-sudoku17.#1.txt.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-mult-sudoku17.#1.txt.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-par-sudoku17.#1.txt.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sudoku-sm/bench-sudoku-sm.bench.parmonad-sudoku-sudoku17.#1.txt.csv};
}{17}{\plotwidthSMP}
}

\begin{figure}
\centering
%\performanceSkelRMDist{44497}{256}{32,64,128,256,512}{544}
%
{\speedupSudokuSM{1000}\label{1231231232}}%
%\hfill%
{\performanceSudokuSM{1000}\label{1231231123122}}
\caption{}
\label{1231231233122}
\end{figure}

@@

\begin{table}
\caption{The benchmarks we use in this paper.}
\label{tab:benches}
\centering
%% something was wrong with separators in table
\renewcommand{\tabcolsep}{1em}
\begin{tabular}{lccll}
\toprule
Name & Area & Type & Origin & Citation \\
\midrule
\rmtest & Mathematics & |parMap+reduce| & Eden & \citet{Lobachev2012}\\
Jacobi sum test & Mathematics & |workpool+reduce| & Eden & \citet{Lobachev2012}\\
Gentleman & Mathematics & |torus| & Eden & \citet{Loogen2012}\\
Sudoku & Puzzle & |parMap| & |Par| Monad & \citet{par-monad}\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\section{Performance results}
\label{sec:benchmarks}

\newcommand{\rmtest}{Rabin--Miller test\xspace}
\newcommand{\sudokutest}{Sudoku test\xspace}
\newcommand{\torustest}{Torus Matrix Multiplication test\xspace}
\newlength{\plotwidthSMP}
\setlength{\plotwidthSMP}{0.39\textwidth}
\newlength{\plotwidthDist}
\setlength{\plotwidthDist}{0.6\textwidth}

@@

\begin{figure}
%\centering
%\performanceSkelRMSM{11213}{64}\hfill%
{\speedupSkelRMSM{11213}{32}}\hfill%
{\speedupSkelRMSM{11213}{64}}
\caption{Relative speedup of \rmtest on a multicore machine. We used the same PArrows-based implementation with
  different backends on the same hardware. Measurements were performed on a single node of the Glasgow
  grid; it has 16 real cores. Input was $2^{11213}-1$, we used 32 (left) or 64 (right)
  tasks. The
  closer to linear speedup the better.}
\label{fig:bench-rm-sm}
\end{figure}

@@

\newcommand{\speedupSudokuSM}[1]{
\speedupplot{Speedup of \sudokutest ``#1''}{Eden CP, Multicore, Par Monad, Par Monad (vanilla)}{16}{4}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-eden-sudoku17.#1.txt.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-mult-sudoku17.#1.txt.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-par-sudoku17.#1.txt.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sudoku-sm/bench-sudoku-sm.bench.parmonad-sudoku-sudoku17.#1.txt.csv};
}{17}{\plotwidthSMP}
}

\begin{figure}
\centering
%\performanceSkelRMDist{44497}{256}{32,64,128,256,512}{544}
%
{\speedupSudokuSM{1000}\label{1231231232}}%
%\hfill%
{\performanceSudokuSM{1000}\label{1231231123122}}
\caption{Relative speedup of \rmtest on a multicore machine. We used the same PArrows-based implementation with
  different backends on the same hardware and the |parMap| version from the |Par| Monad examples \citet{par-monad}\mbcomment{\\originally from http://community.haskell.org/~simonmar/par-tutorial.pdf}. Measurements were performed on a single node of the Glasgow
  grid; it has 16 real cores. Input was a file of $1000$ Sudokus. The
  closer to linear speedup the better.}
\label{1231231233122}
\end{figure}

@@

\begin{table}
\caption{The benchmarks we use in this paper.}
\label{tab:benches}
\centering
%% something was wrong with separators in table
\renewcommand{\tabcolsep}{1em}
\begin{tabular}{lccll}
\toprule
Name & Area & Type & Origin & Citation \\
\midrule
\rmtest & Mathematics & |parMap+reduce| & Eden & \citet{Lobachev2012}\\
Jacobi sum test & Mathematics & |workpool+reduce| & Eden & \citet{Lobachev2012}\\
Gentleman & Mathematics & |torus| & Eden & \citet{Loogen2012}\\
Sudoku & Puzzle & |parMap| & |Par| Monad & \citet{par-monad} \mbcomment{originally from: http://community.haskell.org/~simonmar/par-tutorial.pdf}\\
\bottomrule
\end{tabular}
\end{table}
